---
title: "Result Render"
format: html
editor: visual
---

```{r}
#| label: load-pkg
#| message: false
#| echo: false

pacman::p_load(
  tidyverse,
  kableExtra,
  stringr
)

path_to_res<-file.path(
  dirname(dirname(getwd())),
  "res"
)

denom<-read.csv(file.path(path_to_res,"denom_summ.csv"),stringsAsFactors = F)
var_map<-read.csv(file.path(path_to_res,"var_map.csv"),stringsAsFactors = F)
```

## Overall Descriptive Summary

Oracle Cerner Real World EHR Database recently had released their 2024/08 data in both source and OMOP format. Following the same inclusion and exclusion criteria as below:

-   Delivery events identified by DRG, ICD, or CPT codes defined in [here](https://github.com/gpcnetwork/r21_drivers_mu/blob/main/ref/vs-mmm-delivery.json)

-   Delivery events occurred between 2015-01-01 and 2023-12-31 (de-identified dates)

-   Delivery episode grouping: at least 211 days since the last delivery event in the time period

-   Maternal age between 10 years and 55 years of age

We identified a total of `r denom$N_delivery` pregnancy events among `r denom$N_init_delivery` individuals. We will focus the analysis on the `r denom$N_init_delivery` initial pregnancy events.The following table gives the overall summary of the study cohort, where agegrp1 defines as '\<20 yo', agegrp2 to agegrp5 are 5-years incrementals, and agegrp6 is '\>=40 yo'.

```{r}
#| label: init-summary
#| message: false
#| echo: false

destbl<-read.csv(file.path(path_to_res,"summ_init_cat.csv"),stringsAsFactors = F) %>%
  inner_join(var_map,by="var") %>%
  arrange(var_rklbl,cat) %>%
  mutate(perc = round(prop*100,2)) %>%
  select(var_rklbl, cat, count, perc)

destbl %>%
  kbl() %>% 
  collapse_rows(columns = 1:1, valign = "top") %>%
  kable_paper(full_width = F)
```

Besides the basic demogrphic and facility-level information, we have also included [20 obstetric comorbidity indicators](https://github.com/gpcnetwork/r21_drivers_mu/blob/main/ref/OBCMI_ICD.csv) based on those defined in [OBCMI](https://www.cmqcc.org/research/severe-maternal-morbidity/obstetric-comorbidity-scoring-system). The table below reports column-wise (col_p1,col_p0) and row-wise (row_p1, row_p0) percentages stratified SMM status, \`SMMANY_IND\`:

```{r}
#| label: stratified-summary
#| message: false
#| echo: false

strtbl<-read.csv(file.path(path_to_res,"summ_init_cat_smm.csv"),stringsAsFactors = F) %>%
  group_by(var,cat) %>%
  mutate(rsum = sum(count)) %>%
  ungroup %>%
  mutate(perc = round(count/rsum*100,2),perc_t = 'r') %>%
  select(var,cat,count,SMMANY_IND,perc,perc_t) %>%
  bind_rows(
    read.csv(file.path(path_to_res,"summ_init_cat_smm.csv"),stringsAsFactors = F) %>%
      group_by(var,SMMANY_IND) %>%
      mutate(csum = sum(count)) %>%
      ungroup %>%
      mutate(perc = round(count/csum*100,2),perc_t = 'c') %>%
      select(var,cat,count,SMMANY_IND,perc,perc_t)
  ) %>%
  pivot_wider(
    names_from = c(SMMANY_IND,perc_t),
    values_from = c(count,perc)
  ) %>%
  inner_join(var_map,by="var") %>%
  select(var_rklbl,cat,count_1_r,perc_1_r,perc_1_c,count_0_r,perc_0_r,perc_0_c) %>%
  rename(
    n1 = count_1_r,
    row_p1 = perc_1_r,
    col_p1 = perc_1_c,
    n0 = count_0_r,
    row_p0 = perc_0_r,
    col_p0 = perc_0_c
  ) %>%
  arrange(var_rklbl,cat)

strtbl %>%
  kbl() %>% 
  add_header_above(c(" "," ","w/ SMM"=3,"wo/ SMM"=3)) %>%
  collapse_rows(columns = 1:1, valign = "top") %>%
  kable_paper(full_width = F)
```

## Univariable Logistic Regression

The following table summarized univariate lasso regression results with `SMMANY_IND` as the outcome:

```{r}
#| label: uni-result
#| message: false
#| echo: false

unireg<-read.csv(file.path(path_to_res,"univar_filter_init.csv"),stringsAsFactors = F) %>%
  filter(outcome == "SMMANY_ind") %>%
  left_join(read.csv(file.path(path_to_res,"ohe_map.csv"),stringsAsFactors = F),by=c("var","encoded")) %>%
  mutate(var_orig = gsub("_ohe","",var)) %>%
  inner_join(var_map,by=c("var_orig"="var")) %>%
  mutate(
    pval_print = round(pval,4),
    or_print = round(odds_ratio,3),
    cf_lb_print = round(conf_lower,3),
    cf_ub_print = round(conf_upper,3)
  ) %>%
  arrange(var_rklbl,cat) %>%
  select(var_rklbl,cat,or_print,cf_lb_print,cf_ub_print,pval_print)

unireg %>%
  kbl() %>% 
  collapse_rows(columns = 1:1, valign = "top") %>%
  kable_paper(full_width = F)
```

## Multiple Lasso Logistic Regression Coefficients

The following table summarized multiple lasso regression results with `SMMANY_IND` as the outcome and a restricted list of covariates:

```{r}
#| label: reg-result-sm
#| message: false
#| echo: false

multireg<-read.csv(file.path(path_to_res,"multilasso_smmany_filter_init.csv"),stringsAsFactors = F) %>%
  mutate(
    var = str_remove(feature, "_\\d+$"),
    encoded = str_extract(feature, "(?<=_)\\d+"),
    encoded = as.numeric(encoded)
  ) %>%
  left_join(
    read.csv(file.path(path_to_res,"ohe_map.csv"),stringsAsFactors = F) %>%
      mutate(var = gsub("_ohe","",var)),
    by=c("var","encoded")) %>%
  inner_join(var_map,by="var") %>%
  mutate(
    or_print = round(exp(coef),3),
    cf_lb_print = round(exp(lower),3),
    cf_ub_print = round(exp(upper),3)
  ) %>%
  arrange(var_rklbl,cat) %>%
  select(var_rklbl,cat,or_print,cf_lb_print,cf_ub_print)

multireg %>%
  kbl() %>% 
  collapse_rows(columns = 1:1, valign = "top") %>%
  kable_paper(full_width = F)

```

The following table summarized multiple lasso regression results with `SMMANY_IND` as the outcome and an expansive list of covariates:

```{r}
#| label: reg-result-lg
#| message: false
#| echo: false

multireg2<-read.csv(file.path(path_to_res,"multilasso_smmany_filter_init2.csv"),stringsAsFactors = F) %>%
  mutate(
    var = str_remove(feature, "_\\d+$"),
    encoded = str_extract(feature, "(?<=_)\\d+"),
    encoded = as.numeric(encoded)
  ) %>%
  left_join(
    read.csv(file.path(path_to_res,"ohe_map.csv"),stringsAsFactors = F) %>%
      mutate(var = gsub("_ohe","",var)),
    by=c("var","encoded")
  ) %>%
  inner_join(var_map,by="var") %>%
  mutate(
    or_print = round(exp(coef),3),
    cf_lb_print = round(exp(lower),3),
    cf_ub_print = round(exp(upper),3)
  ) %>%
  arrange(var_rklbl,cat) %>%
  select(var_rklbl,cat,or_print,cf_lb_print,cf_ub_print)

multireg2 %>%
  kbl() %>% 
  collapse_rows(columns = 1:1, valign = "top") %>%
  kable_paper(full_width = F)

```
