---
title: "Result Render"
format: html
editor: visual
---

```{r}
#| label: load-pkg
#| message: false
#| echo: false

pacman::p_load(
  tidyverse,
  kableExtra
)

path_to_res<-file.path(
  dirname(dirname(getwd())),
  "res"
)

denom<-read.csv(file.path(path_to_res,"denom_summ.csv"),stringsAsFactors = F)
```

## Overall Descriptive Summary

Oracle Cerner Real World EHR Database recently had released their 2024/08 data in both source and OMOP format. Following the same inclusion and exclusion criteria as below:
- Delivery events identified by DRG, ICD, or CPT codes defined in: 
- Delivery events occured between 2051-01-01 and 2023-12-31 (de-identified dates) 
- At least 211 days since the last delivery event in the time period
- Maternal age between 10 years and 54 years of age 

We identified a total of `r denom$N_delivery` pregnancy events among `r denom$N_init_delivery` individuals. We will focus the analysis on the `r denom$N_init_delivery` initial pregnancy events. 


```{r}
#| label: init-summary
#| message: false
#| echo: false

destbl<-read.csv(file.path(path_to_res,"summ_init_cat.csv"),stringsAsFactors = F) %>%
  mutate(
    var_print = recode(
      var,
      "agegrp_at_event" = "1.Age",
      "race_source_value" = "2.Race",
      "ethnicity_source_value" = "3.Ethnicity",
      "segment" = "4.Segment",
      "speciality" = "5.Speciality",
      "bed_size" = "6.Bed size",
      "zip_code" = "7.Zip code",
      "death_ind" = "8.Death indicator",
      "SMMANY_ind" = "9.SMM indicator",
      "SMMANY90PCT_ind" = "10.SMM indicator (adjusted by 90 percentile LOS)",
      "BPT_ind" = "11.history of ",
    )
  ) %>%
  arrange(var_print,cat) %>%
  mutate(perc = round(prop*100,2)) %>%
  select(var_print, cat, count, perc)

destbl %>%
  kbl() %>% 
  collapse_rows(columns = 1:1, valign = "top") %>%
  kable_paper(full_width = F)
```


```{r}
#| label: stratified-summary
#| message: false
#| echo: false

strtbl<-read.csv(file.path(path_to_res,"summ_init_cat_smm.csv"),stringsAsFactors = F) %>%
  mutate(
    var_print = recode(
      var,
      "agegrp_at_event" = "1.Age",
      "race_source_value" = "2.Race",
      "ethnicity_source_value" = "3.Ethnicity",
      "segment" = "4.Segment",
      "speciality" = "5.Speciality",
      "bed_size" = "6.Bed size",
      "zip_code" = "7.Zip code",
      "death_ind" = "8.Death indicator",
      "SMMANY_ind" = "9.SMM indicator"
    )
  ) %>%
  arrange(var_print,cat) %>%
  mutate(perc = round(prop*100,2)) %>%
  select(var_print, cat, count, perc, SMMANY_IND) %>%
  pivot_wider(
    names_from = SMMANY_IND,
    values_from = c(count,perc)
  ) %>%
  select(var_print,cat,count_1,perc_1,count_0,perc_0)

strtbl %>%
  kbl() %>% 
  add_header_above(c(" "," ","w/ SMM"=2,"wo/ SMM"=2)) %>%
  collapse_rows(columns = 1:1, valign = "top") %>%
  kable_paper(full_width = F)
```

## Lasso Regression Coefficients

```{r}
#| label: reg-result
#| message: false
#| echo: false

regtbl<-read.csv(file.path(path_to_res,"univar_filter_init.csv"),stringsAsFactors = F) %>%
  filter(outcome == "SMMANY_ind") %>%
  left_join(read.csv(file.path(path_to_res,"ohe_map.csv"),stringsAsFactors = F),by=c("var","encoded")) %>%
  mutate(
    var_print = recode(
      var,
      "age_at_event" = "1a.Age",
      "agegrp_at_event_ohe" = "1b.Age Group",
      "race_source_value_ohe" = "2.Race",
      "ethnicity_source_value_ohe" = "3.Ethnicity",
      "segment_ohe" = "4.Segment",
      "speciality_ohe" = "5.Speciality",
      "bed_size_ohe" = "6.Bed size",
      "zip_code_ohe" = "7.Zip code",
      "los" = "8a.LOS",
      "los1up_ind" = "8b.LOS>1day",
      "los2up_ind" = "8c.LOS>2day",
      "los3up_ind" = "8d.LOS>3day",
      "los4up_ind" = "8e.LOS>4day",
      "los5up_ind" = "8f.LOS>5day",
      "los6up_ind" = "8g.LOS>6day",
      "los7up_ind" = "8h.LOS>7day"
    ),
    pval_print = round(pval,4),
    or_print = round(odds_ratio,3),
    cf_lb_print = round(conf_lower,3),
    cf_ub_print = round(conf_upper,3)
  ) %>%
  arrange(var_print,cat) %>%
  select(var_print,cat,or_print,cf_lb_print,cf_ub_print,pval_print)

regtbl %>%
  kbl() %>% 
  collapse_rows(columns = 1:1, valign = "top") %>%
  kable_paper(full_width = F)

```
